Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-17 paper.qmd
Updated Figure 12

five_c_shaped_proj_tsne_model1_selected <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "a3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")
```

>>>>

five_c_shaped_proj_tsne_model1_selected <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "b3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")
```
